---
title: "Lab 01 - Hello R"
author: "Cat Seitz"
date: "01/14/2023"
output: 
  html_document: 
    theme: cosmo
    fig_width: 5
    highlight: zenburn
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```

## Exercises

### Exercise 1

There are 1846 rows and 3 columns. The variables are dataset, x, and y. 


```{r exercise 1}
datasaurus_dozen %>%
  count(dataset) %>%
  print(13)
```

### Exercise 2


```{r plot-dino, fig.height=6, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```


```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3


```{r plot-star}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")

ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

The correlation coefficient is not much different from the dino correlation coefficient. 

```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))
```

### Exercise 4

Three data points form the circle data seem to be off. 

```{r circle data, fig.height=6, fig.width=6}
circ_data <- datasaurus_dozen %>%
  filter(dataset == "circle")

ggplot(data = circ_data, mapping = aes(x = x, y = y)) +
  geom_point()
```
The correlation coefficient from the circle data is similar to the dino and star correlation coefficients. 

```{r cor-circle}
circ_data %>%
  summarize(r = cor(x, y))
```

### Exercise 5

```{r plot all, fig.height=8, fig.width=6}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+
  geom_point()+
  facet_wrap(~ dataset, ncol = 3) +
  theme(legend.position = "none")
```
```{r cor-all}
datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y)) %>%
  print(13)
```
